Instant Continuation Marks--Just Add $\lambda$

### 2012-10-05 paper.tex
CM monad in it.

>>>>

Expressing continuation marks in a monadic way is simple enough. In Haskell,
\begin{verbatim}
module CM where
import Control.Monad

data CM m a = CM ((Bool,[m]) -> a)

instance Monad (CM m) where
  return x = CM (\_ -> x)
  (CM m) >>= f = CM (\(flag,vs) -> let (CM m') = f (m (False,vs)) in m' (flag,vs))

wcm :: m -> CM m a -> CM m a
wcm v (CM m) = CM (\(f,vs) -> m (True, v:(if f then (tail vs) else vs)))

ccm :: CM m [m]
ccm = CM (\(_,vs) -> vs)

runCM :: CM m a -> a
runCM (CM m) = m (False,[])
\end{verbatim}

\begin{verbatim}
module Main where
import CM

fac :: Int -> CM Int (Int,[Int])
fac 0 = do
  vs <- ccm;
  return (1,vs)

fac n = do
  (acc,vs) <- wcm n (fac (n - 1));
  return (n * acc,vs)

fac_tr :: Int -> Int -> CM Int (Int,[Int])
fac_tr 0 acc = do
  vs <- ccm;
  return (acc,vs)

fac_tr n acc = wcm n (fac_tr (n - 1) (n * acc))

main = do
  print $ runCM (fac 5);
  print $ runCM (fac_tr 5 1)
\end{verbatim}

\begin{verbatim}
(120,[1,2,3,4,5])
(120,[1])
\end{verbatim}
[Say more with less.]
